### 2015-09-29 untitled.tex
edited untitled.tex

The example in Section \ref{sec:unschedulable} can be easily converted to a corresponding deferrable task set. However, it is in general not an easy problem to convert a self-suspending task system into a deferrable task set. Suppose that the system has $k-1$ ordinary sporadic tasks and only one segmented self-suspending task $\tau_k$. Converting a computation segment into a deferrable task requires to derive the \emph{worst-case resume time of a computation segment}, denoted as $R_k^j$ for the $j$-th computation segment of task $\tau_k$. Suppose that the worst-case response time of the $j$-th computation segment of task $\tau_k$ is $W_k^j$. It is not difficult to see that $R_k^1=0$ and $R_k^j = W_k^{j-1}+S_k^{j-1}$ for $j=2,3,\ldots,m_k-1$. So, we need to derive the worst-case response times of the computation segments of task $\tau_k$.

>>>>

The example in Section \ref{sec:unschedulable} can be easily converted to a corresponding deferrable task set. However, it is in general not an easy problem to convert a self-suspending task system into a deferrable task set \emph{precisely}. We can demonstrate the difficulty by looking at a special case. Suppose that the system has $k-1$ ordinary sporadic tasks and only one segmented self-suspending task $\tau_k$. Converting a computation segment into a deferrable task requires to derive the \emph{worst-case resume time of a computation segment}, denoted as $R_k^j$ for the $j$-th computation segment of task $\tau_k$. Suppose that the worst-case response time of the $j$-th computation segment of task $\tau_k$ is $W_k^j$. It is not difficult to see that $R_k^1=0$ and $R_k^j = W_k^{j-1}+S_k^{j-1}$ for $j=2,3,\ldots,m_k-1$. So, we need to derive the worst-case response times of the computation segments of task $\tau_k$.
